MS5130 A3 Clothing_Product_Analysis

### 2024-04-04 MS5130_A3_Clothing_Product_Analysis.qmd
HTML file with embedded resources and qmd file
Updated the qmd code to create html file with embedded resources

---
title: "MS5130 A3 Clothing_Product_Analysis"
author: "Manav"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
toc: true
---

>>>>

---
title: "MS5130 A3 Clothing_Product_Analysis"
author: "Manav"
format:
  html:
    embed-resources: true
    toc: true
    toc-expand: 2
    toc-title: Contents
    toc-depth: 3
editor: visual
editor_options: 
  chunk_output_type: console
---
